\begin{thebibliography}{99}

\bibitem[Acemoglu and Restrepo (2018)]{acemoglu2018race}
Acemoglu, Daron, and Pascual Restrepo. 2018.
``The Race between Man and Machine: Implications of Technology for Growth, Factor Shares, and Employment.''
\textit{American Economic Review}, 108(6): 1488--1542.

\bibitem[Acemoglu and Restrepo (2022)]{acemoglu2022tasks}
Acemoglu, Daron, and Pascual Restrepo. 2022.
``Tasks, Automation, and the Rise in US Wage Inequality.''
\textit{Econometrica}, 90(4): 1973--2016.

\bibitem[Acemoglu, Autor, Hazell, and Restrepo (2022)]{acemoglu2022ai}
Acemoglu, Daron, David Autor, Jonathon Hazell, and Pascual Restrepo. 2022.
``Artificial Intelligence and Jobs: Evidence from Online Vacancies.''
\textit{Journal of Labor Economics}, 40(S1): S293--S340.

\bibitem[Agrawal, Gans, and Goldfarb (2018)]{agrawal2018prediction}
Agrawal, Ajay, Joshua Gans, and Avi Goldfarb. 2018.
``Prediction, Judgment, and Complexity.''
NBER Working Paper No.~24253.

\bibitem[Bolton and Dewatripont (1994)]{bolton1994firm}
Bolton, Patrick, and Mathias Dewatripont. 1994.
``The Firm as a Communication Network.''
\textit{Quarterly Journal of Economics}, 109(4): 809--839.

\bibitem[Brynjolfsson and Hitt (2000)]{brynjolfsson2000beyond}
Brynjolfsson, Erik, and Lorin Hitt. 2000.
``Beyond Computation: Information Technology, Organizational Transformation and Business Performance.''
\textit{Journal of Economic Perspectives}, 14(4): 23--48.

\bibitem[Caplin and Dean (2015)]{caplin2015revealed}
Caplin, Andrew, and Mark Dean. 2015.
``Revealed Preference, Rational Inattention, and Costly Information Acquisition.''
\textit{American Economic Review}, 105(7): 2183--2203.

\bibitem[Dessein and Santos (2006)]{dessein2006adaptive}
Dessein, Wouter, and Tano Santos. 2006.
``Adaptive Organizations.''
\textit{Journal of Political Economy}, 114(5): 956--995.

\bibitem[Dessein, Galeotti, and Santos (2016)]{dessein2016rational}
Dessein, Wouter, Andrea Galeotti, and Tano Santos. 2016.
``Rational Inattention and Organizational Focus.''
\textit{American Economic Review}, 106(6): 1522--1536.

\bibitem[Ely (2017)]{ely2017beeps}
Ely, Jeffrey C. 2017.
``Beeps.''
\textit{American Economic Review}, 107(1): 31--53.

\bibitem[Escud{\'e} and Sinander (2023)]{escude2023slow}
Escud{\'e}, Matteo, and Ludvig Sinander. 2023.
``Slow Persuasion.''
\textit{Theoretical Economics}, 18(1): 129--162.

\bibitem[Garicano (2000)]{garicano2000hierarchies}
Garicano, Luis. 2000.
``Hierarchies and the Organization of Knowledge in Production.''
\textit{Journal of Political Economy}, 108(5): 874--904.

\bibitem[Hadfield-Menell (2021)]{hadfield2021principal}
Hadfield-Menell, Dylan. 2021.
``The Principal-Agent Alignment Problem in Artificial Intelligence.''
PhD diss., University of California, Berkeley.

\bibitem[Holmstr{\"o}m and Milgrom (1991)]{holmstrom1991multitask}
Holmstr{\"o}m, Bengt, and Paul Milgrom. 1991.
``Multitask Principal-Agent Analyses.''
\textit{Journal of Law, Economics, \& Organization}, 7: 24--52.

\bibitem[Ide and Talamas (2025)]{ide2025ai}
Ide, Enrique, and Eduard Talam{\`a}s. 2025.
``Artificial Intelligence in the Knowledge Economy.''
\textit{Journal of Political Economy}, 133(2): 3762--3800.

\bibitem[Kamenica and Gentzkow (2011)]{kamenica2011bayesian}
Kamenica, Emir, and Matthew Gentzkow. 2011.
``Bayesian Persuasion.''
\textit{American Economic Review}, 101(6): 2590--2615.

\bibitem[Lash and Wellington (2008)]{lash2008information}
Lash, Alex, and David Wellington. 2008.
``Information Processing in Hierarchical Organizations.''
\textit{Management Science}, 54(8): 1423--1439.

\bibitem[Lien, Qiu, and Zhong (2019)]{lien2019hierarchies}
Lien, Jaimie W., Xincheng Qiu, and Xiaolan Zhong. 2019.
``Hierarchies and Information Processing in Teams.''
\textit{RAND Journal of Economics}, 50(3): 671--696.

\bibitem[Mackowiak, Mat{\v{e}}jka, and Wiederholt (2023)]{mackowiak2023rational}
Mackowiak, Bartosz, Filip Mat{\v{e}}jka, and Mirko Wiederholt. 2023.
``Rational Inattention: A Review.''
\textit{Journal of Economic Literature}, 61(1): 226--273.

\bibitem[Melumad, Mookherjee, and Reichelstein (1995)]{melumad1995hierarchical}
Melumad, Nahum D., Dilip Mookherjee, and Stefan Reichelstein. 1995.
``Hierarchical Decentralization of Incentive Contracts.''
\textit{RAND Journal of Economics}, 26(4): 654--672.

\bibitem[Noy and Zhang (2023)]{noy2023experimental}
Noy, Shakked, and Whitney Zhang. 2023.
``Experimental Evidence on the Productivity Effects of Generative Artificial Intelligence.''
\textit{Science}, 381(6654): 187--192.

\bibitem[Peng et al.~(2023)]{peng2023impact}
Peng, Sida, Eirini Kalliamvakou, Peter Cihon, and Mert Demirer. 2023.
``The Impact of AI on Developer Productivity: Evidence from GitHub Copilot.''
arXiv preprint arXiv:2302.06590.

\bibitem[Phelps and Ranson (2023)]{phelps2023models}
Phelps, Steve, and Tom Ranson. 2023.
``Of Models and Tin Men: A Multi-Task Principal-Agent Analysis of Large Language Models.''
\textit{Journal of Artificial Intelligence Research}, 77: 1123--1156.

\bibitem[Radner (1993)]{radner1993organization}
Radner, Roy. 1993.
``The Organization of Decentralized Information Processing.''
\textit{Econometrica}, 61(5): 1109--1146.

\bibitem[Renault, Solan, and Vieille (2017)]{renault2017optimal}
Renault, J{\'e}r{\^o}me, Eilon Solan, and Nicolas Vieille. 2017.
``Optimal Dynamic Information Provision.''
\textit{Games and Economic Behavior}, 104: 329--349.

\bibitem[Sims (2003)]{sims2003implications}
Sims, Christopher A. 2003.
``Implications of Rational Inattention.''
\textit{Journal of Monetary Economics}, 50(3): 665--690.

\bibitem[Sims (2006)]{sims2006rational}
Sims, Christopher A. 2006.
``Rational Inattention: Beyond the Linear-Quadratic Case.''
\textit{American Economic Review}, 96(2): 158--163.

\bibitem[Smolin (2021)]{smolin2021dynamic}
Smolin, Alex. 2021.
``Dynamic Evaluation Design.''
\textit{American Economic Journal: Microeconomics}, 13(4): 300--331.

\bibitem[Vaswani et al.~(2017)]{vaswani2017attention}
Vaswani, Ashish, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Lukasz Kaiser, and Illia Polosukhin. 2017.
``Attention Is All You Need.''
\textit{Advances in Neural Information Processing Systems}, 30: 5998--6008.

\bibitem[Williamson (1985)]{williamson1985economic}
Williamson, Oliver E. 1985.
\textit{The Economic Institutions of Capitalism}. New York: Free Press.

\bibitem[Yang and Zhai (2025)]{yang2025ten}
Yang, Zonghao, and Liwen Zhai. 2025.
``Ten Principles of AI Agent Economics.''
arXiv:2505.20273.

\end{thebibliography}
